\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\Large \textbf{Uladzimir Zadarozhny}}\\[0.2cm]
  Senior Manual \& Automation QA / QC Engineer
\end{center}

\section*{Contact Information}
Email: avervovka@gmail.com \\
Phone: +375 29 286 02 38 \\
Viber | Telegram \\
LinkedIn: linkedin.com/in/avervovka

\section*{Professional Summary}
Dedicated and innovative Senior QA Engineer with 6+ years of expertise in both hardware and software testing, across Web, IoT, and consumer electronics. Skilled at designing bulletproof test strategies, driving process improvements, and collaborating with global teams to ensure outstanding product quality.

\section*{Core Competencies}
\begin{itemize}
  \item Manual, Functional, Regression \& Non-Functional Testing
  \item Hardware-Software Integration
  \item API Testing: Postman, Swagger
  \item Automation: Selenium with Python (Pytest)
  \item Programming: Python
  \item Tools: Jira, Confluence, Trello, Youtrack, Redmine, Testrail
  \item Databases: MySQL, DBeaver, Postico
  \item Operating Systems: Linux, macOS, Windows
  \item Other: Git, Bash, CI/CD
\end{itemize}

\section*{Education}
B.Sc. Electrical Engineering, Belarusian State Agrarian Technical University (2013--2018) \\
QA Engineer Course, IT-ACADEMY (2019)

\section*{Languages}
Russian (Native), English (C1), Polish (A2), German (A1)

\section*{References}
Dan Piatrou, Senior Ruby on Rails Developer, +48 789 801 365 \\
Aliaksandr Sabol'ka, QA Lead / Automation Engineer, +375 29 738 78 74 \\
Vladimir Khal'zov, Senior Ruby on Rails Developer, +375 33 344 14 32

\section*{Professional Experience}

\textbf{QA/QC Engineer}, Nero Electronics (Unic Lab), Minsk, Belarus \\
\textit{Dec 2024 -- Present}
\begin{itemize}
  \item Develop and maintain automated Python test scripts for precision measurement instruments, ensuring rigorous product validation.
  \item Manage and update test benches that closely replicate real-world operating environments to guarantee reliability.
  \item Collaborate directly with development teams and clients to meet and exceed quality standards for all delivered solutions.
\end{itemize}

\textbf{Senior QA / QC Engineer}, Freelance, Worldwide \\
\textit{Jun 2023 -- Dec 2024}
\begin{itemize}
  \item Performed functional and API testing of modern educational web platforms using Postman and Swagger.
  \item Conducted full-cycle hardware and software testing for a massage robot project targeting a Dubai-based client.
  \item Ensured timely detection and clear documentation of defects, contributing directly to product improvements and user satisfaction.
\end{itemize}

\textbf{Senior QA / QC Engineer}, Rozum Robotics, Minsk, Belarus \\
\textit{Sep 2022 -- Jun 2023}
\begin{itemize}
  \item Introduced and enforced quality standards for robotic products, enhancing their reliability and compliance with requirements.
  \item Mentored junior QA engineers, promoting the use of advanced testing methodologies and effective tools.
  \item Maintained hardware test benches in top condition to enable accurate and repeatable testing procedures.
\end{itemize}

\textbf{Senior QA / QC Engineer}, Clever Labs, Minsk, Belarus \\
\textit{Apr 2021 -- Sep 2022}
\begin{itemize}
  \item Led end-to-end testing for a complex US-based insurance web application, ensuring stability and compliance.
  \item Worked directly with clients and internal teams, streamlining communication and delivering crisp technical documentation.
  \item Optimized QA processes, significantly reducing defect resolution time and accelerating release cycles.
\end{itemize}

\textbf{QA/QC Engineer}, Zorachka, Minsk, Belarus \\
\textit{Oct 2019 -- Apr 2021}
\begin{itemize}
  \item Designed and executed comprehensive test scenarios for a multifunctional smart camera, maintaining high quality standards.
  \item Performed thorough mobile application testing, identifying and documenting critical issues for rapid resolution.
  \item Developed and maintained detailed technical documentation to support developers and end-users alike.
\end{itemize}

\section*{Certificates}
Selenium Python, Python OOP, HTML \& CSS, Python Programming, Python Generation, Python by Sergei Balakirev

\vfill
\begin{center}
  \textcopyright{} 2025 Uladzimir Zadarozhny. All rights reserved.
\end{center}

\end{document}